```{r, echo = FALSE, results = "hide"}
vi <-signif(runif(1, 10, 40), 3) # speed in m/s
h <- signif(runif(1, 1, 10), 3) # height of bridge in m
g <- 9.8 # acceleration due to gravity in m/s^2

t <- sqrt(2 * h / g) # time to fall in the water in s
r <- vi * t # horizontal range of the rock in m
  
sc <- num_to_schoice(r, delta = 0.1, digits = 1, format = FALSE)
sc$questions <- sprintf("%g m", sc$questions)
```

Question
========
A person throws a rock horizontally, with an initial velocity of `r vi` m/s, from a bridge. It falls `r h` m to the water below. How far does it travel horizontally before striking the water?

```{r questionlist, echo = FALSE, results = "asis"}
answerlist(sc$questions, markup = "markdown")
```

Solution
========
First analyze the vertical motion to find the time it takes the rock to hit the water using the formula $d = \frac{1}{2} a t^2$

$$t = \sqrt{\frac{2d}{a}} = \sqrt{\frac{2(`r h` \,\mathsf{m})}{`r g` \,\mathsf{m/s^2}}} = `r t` \,\mathsf{s}$$
Then, use the time to figure out how far the rock travels horizontally (recall that the horizontal velocity is constant).

$$d_x = v_x t = (`r vi` \,\mathsf{m/s})(`r t` \,\mathsf{s}) = `r signif(r, 3)` \,\mathsf{m}$$

Meta-information
================
exname: calculate range of a horizontal projectile with initial height
extype: schoice
exsolution: `r mchoice2string(sc$solutions)`
exshuffle: 4
