```{r, echo = FALSE, results = "hide"}
vi <- sample(30:120, 1) # initial speed in km/h
a <- 5 # acceleration is m/s^2

d <- (vi / 3.6) ^ 2 / 2 / a
distractors <- c(vi / 3.6 / 2 / a, vi^2 / 2 / a)

sc <- num_to_schoice(d, wrong = distractors, digits = 0, format = FALSE)

sc$questions <- sprintf("\\SI{%g}{m}", sc$questions)
```

Question
========
A car with good tires on a dry road can decelerate at about \SI{5.0}{m/s^2} when braking. If the car travels with an initial velocity of \SI{`r vi`}{km/h} and brakes under such conditions, what distance would it travel before it stops?

```{r questionlist, echo = FALSE, results = "asis"}
answerlist(sc$questions, markup = "markdown")
```

Solution
========
First, convert the initial velocity to \si{m/s}.

$$\SI{`r vi`}{km/h} \times \frac{\SI{1000}{m}}{\SI{1}{km}} \times \frac{\SI{1}{h}}{\SI{3600}{s}} = \SI{`r vi/3.6`}{m/s}$$

Then, use the formula $v_f^2 = v_i^2 + 2ad$ with $v_f = 0$ and $a = \SI{-5}{m/s^2}$.

$$d = \frac{-v_i^2}{2a} = \frac{-(\SI{`r vi/3.6`}{m/s})^2}{2(\SI{-5.0}{m/s^2})} = \SI{`r signif(d, 2)`}{m}$$

Meta-information
================
exname: calculate car braking distance
extype: schoice
exsolution: `r mchoice2string(sc$solutions)`
exshuffle: 4
