```{r, echo = FALSE, results = "hide"}
sf <- 3 # number of significant figures to use
vf <- signif(runif(1, 200, 300), sf) # final launch speed in km/h
t <- signif(runif(1, 2, 3), sf) # time in s

d <- (vf / 3.6) / 2 * t
distractors <- c(vf / 3.6 * t, vf / 2 * t)

sc <- num_to_schoice(d, wrong = distractors, format = FALSE)

sc$questions <- sapply(sc$questions, signif, sf)
sc$questions <- paste("$", gsub("^ +", "", sc$questions), "\\text{ m}$", sep = "")
```

Question
========
A fighter plane is launched from a catapult on an aircraft carrier. Starting from rest, it reaches a speed of `r vf` km/h in `r t` seconds. Assuming constant acceleration, what is the length of the aircraft catapult?

```{r questionlist, echo = FALSE, results = "asis"}
answerlist(sc$questions, markup = "markdown")
```

Solution
========
First, convert the final speed to m/s:

$$v_f = `r vf` \text{ km/h} \times \frac{1000 \text{ m}}{1 \text{ km}} \times \frac{1 \text{ h}}{3600 \text{ s}} = `r signif(vf/3.6, sf)` \text{ m/s}$$
Then, use the formula for constant acceleration:
$$d = \frac{1}{2}(v_i + v_f)t = \frac{1}{2} (0 + `r signif(vf/3.6, sf)` \text{ m/s})(`r t` \text{ s}) = `r signif(d, sf)` \text{ m}$$ 

Meta-information
================
exname: calculate d given initial and final velocities on an aircraft carrier
extype: schoice
exsolution: `r mchoice2string(sc$solutions)`
exshuffle: 4
