```{r, echo = FALSE, results = "hide"}
sf <- 3 # significant digits to use
t <- sample(2:6, 1) # time to stop in seconds
v_avg <- sample(30:60, 1) # initial speed in km/h

a <- -2 * v_avg / t
dis <- c(-v_avg / t)

sc <- num_to_schoice(a, wrong = dis, format = FALSE)
sc$questions <- sapply(sc$questions, signif, sf)
sc$questions <- sprintf("\\SI{%g}{km/h/s}", sc$questions)
```

Question
========
A car slows down uniformly and comes to a stop after $\SI{`r t`}{s}$. The car's average velocity during this motion was $\SI{`r v_avg`}{km/h}$. What was the car's acceleration while slowing down?

```{r questionlist, echo = FALSE, results = "asis"}
answerlist(sc$questions, markup = "markdown")
```

Solution
========
Since the car's acceleration was uniform and the final velocity was zero, the initial velocity is double the average velocity.

$$v_{avg} = \frac{v_i + v_f}{2} = \frac{v_i}{2}$$
$$v_i = 2 v_{avg} = \SI{`r 2*v_avg`}{km/h}$$

The acceleration is the change in speed divided by the time.
$$a = \frac{v_f - v_i}{t} = \frac{0 - \SI{`r 2*v_avg`}{km/h}}{\SI{`r t`}{s}} = \SI{`r signif(a, 3)`}{km/h/s}$$

Meta-information
================
exname: calculate acceleration given time and average velocity of a car stopping
extype: schoice
exsolution: `r mchoice2string(sc$solutions)`
exshuffle: 4
