```{r calculate-v-given-d-t, echo = FALSE, results = "hide"}
sf <- 3 # significant figures to use
t <- signif(runif(1, 1, 9), 3) # time in s
g <- 9.8 # acceleration due to gravity in m/s^2

vi <- g * t / 2

sc <- num_to_schoice(vi, format = FALSE, digits = 1)
sc$questions <- sprintf("%g m/s", sc$questions)
```

Question
========
A ball tossed straight up returns to its starting point in `r t` s. What was its initial speed? Ignore air resistance.

```{r questionlist, echo = FALSE, results = "asis"}
answerlist(sc$questions, markup = "markdown")
```

Solution
========
The final velocity is equal to the initial velocity, but in the opposite direction ($v_f = -v_i$). Substitute this into the equation $v_f = v_i + at$ and solve for $vi$:

$$-v_i = v_i + at$$
$$-2v_i = at$$
$$vi = -\frac{at}{2} = -\frac{(-9.8 \,\mathsf{m/s^2})(`r t` \,\mathsf{s})}{2} = `r signif(vi, 3)` \,\mathsf{m/s}$$


Meta-information
================
exname: calculate initial velocity given time 1d projectile
extype: schoice
exsolution: `r mchoice2string(sc$solutions)`
exshuffle: 4
