```{r}
options(scipen=999)
```


Question
========
A light-year (ly) is the distance that light travels in vacuum in one year.  
The speed of light is $3 \times 10^8 \,\mathsf{m/s}$. How many miles are there in a light-year?


Answerlist
----------
* $5.88 \times 10^{12} \,\mathsf{mi}$
* $9.46 \times 10^{12} \,\mathsf{mi}$
* $5.88 \times 10^{15} \,\mathsf{mi}$
* $9.46 \times 10^{15} \,\mathsf{mi}$


Solution
========
Use the formula for constant velocity motion and convert to the desired units.

```{r, echo=FALSE}
t <- 365*24*60*60
d <- 3E8 * t
```
$$(\SI{1}{yr}) \left(\frac{\SI{365}{days}}{\SI{1}{yr}}\right) \left(\frac{\SI{24}{h}}{\SI{1}{day}}\right) \left(\frac{\SI{60}{min}}{\SI{1}{h}}\right) \left(\frac{\SI{60}{s}}{\SI{1}{min}}\right) = \SI{`r sprintf("%g", t)`}{s}$$

$$ d = vt = (\SI{3.00E8}{m/s})(\SI{`r sprintf("%g", t)`}{s}) = \SI{`r sprintf("%g", d)`}{m}$$
$$(\SI{`r sprintf("%g", d)`}{m}) \left(\frac{\SI{1}{mi}}{\SI{1.609E3}{m}}\right) = \SI{`r sprintf("%g", signif(d/1.609E3, 3))`}{mi}$$

Meta-information
================
exname: light year distance in miles
extype: schoice
exsolution: 1000
exshuffle: 4
