```{r, echo = FALSE, results = "hide"}
sf <- 3 # significant digits to use
a <- sample(1:6, 1) # acceleration in m/s/s
vi <- sample(10:50, 1) # initial speed in km/h
vf <- sample(80:120, 1) # final speed in km/h

ans <- (vf - vi) / 3.6 / a
dis <- c((vf - vi) / a)

sc <- num_to_schoice(ans, wrong = dis, delta = 0.1, range(ans/10, ans*10), format = FALSE)
sc$questions <- sapply(sc$questions, signif, sf)
sc$questions <- sprintf("%g s", sc$questions)
```

Question
========
A car accelerates from `r vi` km/h to `r vf` km/h, at an average rate of $`r a` \,\mathsf{m/s^2}$. How much time does it take to complete this speed increase?

```{r questionlist, echo = FALSE, results = "asis"}
answerlist(sc$questions, markup = "markdown")
```

Solution
========
First, convert the speeds from km/h to m/s:

```{r, echo = FALSE, results = "hide"}
vi_ms <- signif(vi / 3.6, sf)
vf_ms <- signif(vf / 3.6, sf)
```

$$v_i = `r vi` \,\mathsf{km/h} \times \frac{1 \,\mathsf{h}}{3600 \,\mathsf{s}} \times \frac{1000 \,\mathsf{m}}{1 \,\mathsf{km}} = `r vi_ms` \,\mathsf{m/s}$$
$$v_f = `r vf` \,\mathsf{km/h} \times \frac{1 \,\mathsf{h}}{3600 \,\mathsf{s}} \times \frac{1000 \,\mathsf{m}}{1 \,\mathsf{km}} = `r vf_ms` \,\mathsf{m/s}$$


Then, use the formula for constant acceleration motion.

$$t = \frac{v_f - v_i}{a} = \frac{`r vf_ms` \,\mathsf{m/s} - `r vi_ms` \,\mathsf{m/s}}{`r a` \,\mathsf{m/s^2}} = `r signif(ans, 3)` \,\mathsf{s}$$

Meta-information
================
exname: calculate t given a, vi, and vf in km/h
extype: schoice
exsolution: `r mchoice2string(sc$solutions)`
exshuffle: 4
