```{r, echo = FALSE, results = "hide"}
sf <- 3 # number of significant figures to use
vf <- signif(runif(1, 200, 300), sf) # final launch speed in km/h
t <- signif(runif(1, 2, 3), sf) # time in s

d <- (vf / 3.6) / 2 * t
distractors <- c(vf / 3.6 * t, vf / 2 * t)

sc <- num_to_schoice(d, wrong = distractors, format = FALSE)

sc$questions <- sapply(sc$questions, signif, sf)
sc$questions <- sprintf("\\SI{%g}{m}", sc$questions)
```

Question
========
A fighter plane is launched from a catapult on an aircraft carrier. Starting from rest, it reaches a speed of \SI{`r vf`}{km/h} in \SI{`r t`}{s}. Assuming constant acceleration, what is the length of the aircraft catapult?

```{r questionlist, echo = FALSE, results = "asis"}
answerlist(sc$questions, markup = "markdown")
```

Solution
========
First, convert the final speed to \unit{m/s}:

$$v_f = \SI{`r vf`}{km/h} \times \frac{\SI{1000}{m}}{\SI{1}{km}} \times \frac{\SI{1}{h}}{\SI{3600}{s}} = \SI{`r signif(vf/3.6, sf)`}{m/s}$$
Then, use the formula for constant acceleration:
$$d = \frac{1}{2}(v_i + v_f)t = \frac{1}{2} (0 + \SI{`r signif(vf/3.6, sf)`}{m/s})(\SI{`r t`}{s}) = \SI{`r signif(d, sf)`}{m}$$ 

Meta-information
================
exname: calculate d given initial and final velocities on an aircraft carrier
extype: schoice
exsolution: `r mchoice2string(sc$solutions)`
exshuffle: 4
