```{r, echo = FALSE, results = "hide"}
vi <- sample(10:99, 1) # initial speed in m/s
angle <- sample(10:80, 1) # angle of launch from the horizontal in degrees
g <- 9.8 # acceleration due to gravity in m/s^2

t <- 2 * vi * sin(angle * pi / 180) / g # time for golf ball to hit the ground
r <- vi * cos(angle * pi / 180) * t # horizontal range of the rock in m
  
sc <- num_to_schoice(r, delta = 1, digits = 0, format = FALSE)
sc$questions <- sprintf("%g m", sc$questions)
```

Question
========
A golf ball is hit with an initial velocity of `r fmt(vi,1)` m/s at an angle of `r fmt(angle,1)`° above the horizontal. What is its range (horizontal distance before hitting the ground)? Ignore air resistance and assume a flat golf course.

```{r questionlist, echo = FALSE, results = "asis"}
answerlist(sc$questions, markup = "markdown")
```

Solution
========
First, analyze the vertical motion to find the time it takes the ball to hit the ground using the formula $v_f = v_i + at$ with $v_f = -v_i$:

$$t = -\frac{2v_i}{a} = -\frac{2 (`r vi` \,\mathsf{m/s}) \sin(`r angle`^\circ)}{`r -g` \,\mathsf{m/s^2}} = `r t` \,\mathsf{s}$$
Then, use the time to figure out how far the ball travels horizontally (recall that the horizontal velocity is constant).

$$d_x = v_x t = (`r vi` \,\mathsf{m/s})(\cos(`r angle`^\circ))(`r t` \,\mathsf{s}) = `r signif(r, 3)` \,\mathsf{m}$$

Meta-information
================
exname: calculate range of a horizontal projectile
extype: schoice
exsolution: `r mchoice2string(sc$solutions)`
exshuffle: 4
