```{r, echo = FALSE, results = "hide"}
vi <-signif(runif(1, 1, 40), 3) # speed in m/s
h <- signif(runif(1, 1, 40), 3) # height of bridge in m
g <- 9.8 # acceleration due to gravity in m/s^2

# assigning down as positive
a <- 0.5 * g
b <- vi
c <- -h

t <- (-b + sqrt(b^2 - 4*a*c)) / (2 * a)

sc <- num_to_schoice(t, delta = 0.01, digits = 2, format = FALSE)
sc$questions <- sprintf("%g s", sc$questions)
```

Question
========
A person throws a rock straight down from a bridge with an initial speed of `r vi` m/s. It falls `r h` m to the water below. How much time does it take for the rock to hit the water?

```{r questionlist, echo = FALSE, results = "asis"}
answerlist(sc$questions, markup = "markdown")
```

Solution
========
Use the quadratic formula to solve the equation $h = \frac{1}{2} g t^2 + v_i t$ for $t$.

$$\frac{1}{2} g t^2 + v_i t - h = 0$$
$$a = \frac{1}{2} g = \frac{1}{2} (`r g` \,\mathsf{m/s^2}) = `r a` \,\mathsf{m/s^2}, b = v_i = `r vi` \,\mathsf{m/s}, c = -h = `r -h` \,\mathsf{m}$$

$$t = \frac{-b + \sqrt{b^2 - 4ac}}{2a} = `r fmt(t)` \,\mathsf{s}$$


Meta-information
================
exname: calculate time given initial velocity and height of a 1d projectile
extype: schoice
exsolution: `r mchoice2string(sc$solutions)`
exshuffle: 4
