```{r, echo = FALSE, results = "hide"}
sf <- 3 # significant digits to use
t <- sample(2:6, 1) # time to stop in seconds
v_avg <- sample(30:60, 1) # initial speed in km/h

a <- -2 * v_avg / t
dis <- c(-v_avg / t)

sc <- num_to_schoice(a, wrong = dis, format = FALSE)
sc$questions <- sapply(sc$questions, signif, sf)
sc$questions <- paste("$", gsub("^ +", "", sc$questions), "\\text{ km/h/s}$", sep = "")
```

Question
========
A car decelerates uniformly and comes to a stop after `r t` seconds. The car's average velocity during the deceleration was `r v_avg` km/h. What was the car's acceleration while slowing down?

```{r questionlist, echo = FALSE, results = "asis"}
answerlist(sc$questions, markup = "markdown")
```

Solution
========
Since the car's acceleration was uniform and the final velocity was zero, the initial velocity is double the average velocity.

$$v_{avg} = \frac{v_i + v_f}{2} = \frac{v_i}{2}$$
$$v_i = 2 v_{avg} = `r 2*v_avg` \text{ km/h}$$

The acceleration is the change in speed divided by the time.
$$a = \frac{v_f - v_i}{t} = \frac{0 - `r 2*v_avg`\text{ km/h}}{`r t`\text{ s}} = `r signif(a, 3)` \text{ km/h/s}$$

Meta-information
================
exname: calculate acceleration given time and average velocity of a car stopping
extype: schoice
exsolution: `r mchoice2string(sc$solutions)`
exshuffle: 4
