```{r, echo = FALSE, results = "hide"}
vi <- sample(30:120, 1) # initial speed in km/h
a <- 5 # acceleration is m/s^2

d <- (vi / 3.6) ^ 2 / 2 / a
distractors <- c(vi / 3.6 / 2 / a, vi^2 / 2 / a)

sc <- num_to_schoice(d, wrong = distractors, digits = 0, format = FALSE)

sc$questions <- sprintf("%g m", sc$questions)
```

Question
========
A car with good tires on a dry road can decelerate at about $5.0 \,\mathsf{m/s^2}$ when braking. If the car travels with an initial velocity of $`r vi` \,\mathsf{km/h}$ and brakes under such conditions, what distance would it travel before it stops?

```{r questionlist, echo = FALSE, results = "asis"}
answerlist(sc$questions, markup = "markdown")
```

Solution
========
First, convert the initial velocity to m/s:

$$`r vi` \,\mathsf{km/h} \times \frac{1000 \,\mathsf{m}}{1 \,\mathsf{km}} \times \frac{1 \,\mathsf{h}}{3600 \,\mathsf{s}} = `r vi/3.6` \,\mathsf{m/s}$$

Then, use the formula $v_f^2 = v_i^2 + 2ad$ with $v_f = 0$ and $a = -5 \,\mathsf{m/s^2}$.

$$d = \frac{-v_i^2}{2a} = \frac{-(`r vi/3.6` \,\mathsf{m/s})^2}{2(-5.0 \,\mathsf{m/s^2})} = `r signif(d, 2)` \,\mathsf{m}$$

Meta-information
================
exname: calculate car braking distance
extype: schoice
exsolution: `r mchoice2string(sc$solutions)`
exshuffle: 4
