```{r, echo = FALSE, results = "hide"}
# use the same graphics type (pdf, svg, png) as the current xweave() call
typ <- match_exams_device()

# tikz velocity-time graph
tikz_graph <- "\\begin{tikzpicture}
                        \\draw[-Stealth] node[anchor=east] {$0$} (0,0) -- (10, 0) node[anchor=west] {time};
                        \\draw[Stealth-Stealth] (0,-2) -- (0,2) node[anchor=east] {position};
                        \\draw[red, ultra thick] (0,0) -- (3, -2) -- (8, 1) -- (9.8, 0);
                        \\node at (3,0) [anchor=south] {A};
                        \\node at (6,0) [anchor=south] {B};
                        \\node at (8,0) [anchor=south] {C};
                        \\node at (10,0) [anchor=south] {D};
                \\end{tikzpicture}"
```

Question
========
The motion of an object is described by the following position-time graph. At which point in time is the magnitude of the object's displacement at a maximum?

```{r, echo = FALSE, results = "asis"}
include_tikz(tikz_graph, name = "p-t-graph", format = typ, library = c("arrows.meta"), packages="siunitx")
```


Answerlist
----------
* Point A
* Point B
* Point C
* Point D


Solution
========
The displacement is maximum when the position is furthest away from the starting position.


Meta-information
================
exname: position time graph max displacement
extype: schoice
exsolution: 1000
