```{r p-t-graph-obj-at-rest, echo = FALSE, results = "hide"}
# use the same graphics type (pdf, svg, png) as the current xweave() call
typ <- match_exams_device()

# tikz velocity-time graph
tikz_graph_A <- "\\begin{tikzpicture} 
                        \\draw[->] (0,-1.5) node[anchor=east] {$0$} -- (3, -1.5) node[anchor=west] {$t$};
                        \\draw[->] (0,-1.5) -- (0,1.5) node[anchor=east] {$x$};,
                        \\draw[red, ultra thick] (0,0) -- (3, 0);),
                \\end{tikzpicture}"

tikz_graph_B <- "\\begin{tikzpicture}
                        \\draw[->] (0,-1.5) node[anchor=east] {$0$} -- (3, -1.5) node[anchor=west] {$t$};
                        \\draw[->] (0,-1.5) -- (0,1.5) node[anchor=east] {$x$};
                        \\draw[red, ultra thick] (1.5,-1.5) -- (1.5, 1.5);
                \\end{tikzpicture}"

tikz_graph_C <- "\\begin{tikzpicture}
                        \\draw[->] (0,-1.5) node[anchor=east] {$0$} -- (3, -1.5) node[anchor=west] {$t$};
                        \\draw[->] (0,-1.5) -- (0,1.5) node[anchor=east] {$x$};
                        \\draw[red, ultra thick] (0,-1.5) -- (3, 1.5);
                \\end{tikzpicture}"

tikz_graph_D <- "\\begin{tikzpicture}
                        \\draw[->] (0,-1.5) node[anchor=east] {$0$} -- (3,-1.5) node[anchor=west] {$t$};
                        \\draw[->] (0,-1.5) -- (0,1.5) node[anchor=east] {$x$};
                        \\draw[red, ultra thick] (0,1.2) -- (2.7, -1.5);
                \\end{tikzpicture}"

choices <- c("Graph A", "Graph B", "Graph C", "Graph D")

# Generate all graphs
graphs <- c(
  include_tikz(tikz_graph_A, name = "p-t-graph-obj-at-rest-A", markup = "none", format = typ),
  include_tikz(tikz_graph_B, name = "p-t-graph-obj-at-rest-B", markup = "none", format = typ),
  include_tikz(tikz_graph_C, name = "p-t-graph-obj-at-rest-C", markup = "none", format = typ),
  include_tikz(tikz_graph_D, name = "p-t-graph-obj-at-rest-D", markup = "none", format = typ)
)

# Randomize graphs and find the correct answer (original graph A)
rand_ord <- sample(1:4)
graphs <- graphs[rand_ord]
sol <- c(TRUE, rep(FALSE, 3))
sol <- sol[rand_ord]
```

Question
========

Which position-time graph represents an object at rest?

|            Graph A            |             Graph B           |             Graph C           |             Graph D           |
|:-----------------------------:|:-----------------------------:|:-----------------------------:|:-----------------------------:|
| ![](`r graphs[1]`){width=3cm} | ![](`r graphs[2]`){width=3cm} | ![](`r graphs[3]`){width=3cm} | ![](`r graphs[4]`){width=3cm} |


```{r, echo = FALSE, results = "asis"}
answerlist(choices, markup = "markdown")
```


Solution
========
An object at rest has zero velocity so the slope of its position-time graph must have a slope of zero (horizontal line).


Meta-information
================
exname: position time graph object at rest
extype: schoice
exsolution: `r mchoice2string(sol)`
