```{r v-t-graph-postive-acc, echo = FALSE, results = "hide"}
# use the same graphics type (pdf, svg, png) as the current xweave() call
typ <- match_exams_device()

# tikz velocity-time graph
tikz_graph_A <- "\\begin{tikzpicture}
                        \\draw[->] node[anchor=east] {$0$} (0,0) -- (3, 0) node[anchor=west] {$t$};
                        \\draw[<->] (0,-1.5) -- (0,1.5) node[anchor=east] {$v$};
                        \\draw[red, ultra thick] (0,-1.4) .. controls (1,-1.4) and (2, -1.4) .. (2.9,0);
                \\end{tikzpicture}"

tikz_graph_B <- "\\begin{tikzpicture}
                        \\draw[->] node[anchor=east] {$0$} (0,0) -- (3, 0) node[anchor=west] {$t$};
                        \\draw[<->] (0,-1.5) -- (0,1.5) node[anchor=east] {$v$};
                        \\draw[red, ultra thick] (0,0) .. controls (1,0.5) and (2, 1) .. (2.9,1.5);
                \\end{tikzpicture}"

tikz_graph_C <- "\\begin{tikzpicture}
                        \\draw[->] node[anchor=east] {$0$} (0,0) -- (3, 0) node[anchor=west] {$t$};
                        \\draw[<->] (0,-1.5) -- (0,1.5) node[anchor=east] {$v$};
                        \\draw[red, ultra thick] (0,0) -- (2.9, -1.4);
                \\end{tikzpicture}"

tikz_graph_D <- "\\begin{tikzpicture}
                        \\draw[->] node[anchor=east] {$0$} (0,0) -- (3,0) node[anchor=west] {$t$};
                        \\draw[<->] (0,-1.5) -- (0,1.5) node[anchor=east] {$v$};
                        \\draw[red, ultra thick] (0,0) .. controls (0.5,1.5) and (1,1.5) .. (2.9,1.5);
                \\end{tikzpicture}"

choices <- c("Graph A", "Graph B", "Graph C", "Graph D")

# Generate all graphs
graphs <- c(
  include_tikz(tikz_graph_A, name = "v-t-graph-postive-acc-A", markup = "none", format = typ),
  include_tikz(tikz_graph_B, name = "v-t-graph-postive-acc-B", markup = "none", format = typ),
  include_tikz(tikz_graph_C, name = "v-t-graph-postive-acc-C", markup = "none", format = typ),
  include_tikz(tikz_graph_D, name = "v-t-graph-postive-acc-D", markup = "none", format = typ)
)

# Randomize graphs and find the correct answer (original graph A)
rand_ord <- sample(1:4)
graphs <- graphs[rand_ord]
sol <- c(TRUE, rep(FALSE, 3))
sol <- sol[rand_ord]
```

Question
========

Which velocity-time graph represents the motion of an object that is slowing down?

|            Graph A            |             Graph B           |             Graph C           |             Graph D           |
|:-----------------------------:|:-----------------------------:|:-----------------------------:|:-----------------------------:|
| ![](`r graphs[1]`){width=3cm} | ![](`r graphs[2]`){width=3cm} | ![](`r graphs[3]`){width=3cm} | ![](`r graphs[4]`){width=3cm} |


```{r, echo = FALSE, results = "asis"}
answerlist(choices, markup = "markdown")
```


Solution
========
Slowing down is represented by a line approaching the time axis on a velocity-time graph.


Meta-information
================
exname: velocity time graph slowing down
extype: schoice
exsolution: `r mchoice2string(sol)`
