```{r v-t-graph-postive-acc, echo = FALSE, results = "hide"}
# use the same graphics type (pdf, svg, png) as the current xweave() call
typ <- match_exams_device()

# tikz velocity-time graph
tikz_graph_A <- "\\begin{tikzpicture}
                        \\draw[->] node[anchor=east] {$0$} (0,0) -- (3, 0) node[anchor=west] {$t$};
                        \\draw[<->] (0,-1.5) -- (0,1.5) node[anchor=east] {$v$};
                        \\draw[red, ultra thick] (0,-1.4) -- (2.9, 0);
                \\end{tikzpicture}"

tikz_graph_B <- "\\begin{tikzpicture}
                        \\draw[->] node[anchor=east] {$0$} (0,0) -- (3, 0) node[anchor=west] {$t$};
                        \\draw[<->] (0,-1.5) -- (0,1.5) node[anchor=east] {$v$};
                        \\draw[red, ultra thick] (0,1) -- (3, 1);
                \\end{tikzpicture}"

tikz_graph_C <- "\\begin{tikzpicture}
                        \\draw[->] node[anchor=east] {$0$} (0,0) -- (3, 0) node[anchor=west] {$t$};
                        \\draw[<->] (0,-1.5) -- (0,1.5) node[anchor=east] {$v$};
                        \\draw[red, ultra thick] (0,0) -- (3, -1.5);
                \\end{tikzpicture}"

tikz_graph_D <- "\\begin{tikzpicture}
                        \\draw[->] node[anchor=east] {$0$} (0,0) -- (3,0) node[anchor=west] {$t$};
                        \\draw[<->] (0,-1.5) -- (0,1.5) node[anchor=east] {$v$};
                        \\draw[red, ultra thick] (0,1.4) -- (2.9, 0);
                \\end{tikzpicture}"

choices <- c("Graph A", "Graph B", "Graph C", "Graph D")

# Generate all graphs
graphs <- c(
  include_tikz(tikz_graph_A, name = "v-t-graph-postive-acc-A", markup = "none", format = typ),
  include_tikz(tikz_graph_B, name = "v-t-graph-postive-acc-B", markup = "none", format = typ),
  include_tikz(tikz_graph_C, name = "v-t-graph-postive-acc-C", markup = "none", format = typ),
  include_tikz(tikz_graph_D, name = "v-t-graph-postive-acc-D", markup = "none", format = typ)
)

# Randomize graphs and find the correct answer (original graph A)
rand_ord <- sample(1:4)
graphs <- graphs[rand_ord]
sol <- c(TRUE, rep(FALSE, 3))
sol <- sol[rand_ord]
```

Question
========

Which velocity-time graph represents motion with constant positive acceleration?

|            Graph A            |             Graph B           |             Graph C           |             Graph D           |
|:-----------------------------:|:-----------------------------:|:-----------------------------:|:-----------------------------:|
| ![](`r graphs[1]`){width=3cm} | ![](`r graphs[2]`){width=3cm} | ![](`r graphs[3]`){width=3cm} | ![](`r graphs[4]`){width=3cm} |


```{r, echo = FALSE, results = "asis"}
answerlist(choices, markup = "markdown")
```


Solution
========
Acceleration is the slope of the velocity-time graph. Therefore, the correct answer is the graph with the positive slope. Note that for positive acceleration it does not matter if the velocity is always negative as long as the slope is positive.


Meta-information
================
exname: velocity time graph positive acceleration
extype: schoice
exsolution: `r mchoice2string(sol)`
