```{r, echo = FALSE, results = "hide"}
options(scipen=999)
d_load <- sample(2:5, 1) # distance from fulcrum to load in metres
d_effort <- d_load + sample(1:5, 1) # distance from fulcrum to effort in metres
f_effort <- 100 * sample(1:10, 1) # effort force in newtons

max_load <- d_effort / d_load * f_effort
s <- d_load + d_effort
distractors <- c(d_load / d_effort, s / d_load, s / d_effort, d_load / s, d_effort / s) * f_effort

sc <- num_to_schoice(max_load, wrong = distractors, delta = max_load/100, format = FALSE)
sc$questions <- sprintf("$\\SI{%g}{\\N}$", signif(sc$questions, 3))

# use the same graphics type (pdf, svg, png) as the current xweave() call
typ <- match_exams_device()

## tikz beam graphic
tikz <- c("\\begin{tikzpicture}",
    sprintf("\\draw[very thick] (0, 0.5) -- (%d, 0.5);", d_effort + d_load),
    sprintf("\\draw[very thick] (%f, 0.5) -- (%f, 0) -- (%f, 0) -- cycle;", d_effort, d_effort + 0.5, d_effort - 0.5),
    sprintf("\\draw[very thick] (%f, 1) rectangle (%f, 0.5);", s-0.25, s+0.25),
    sprintf("\\draw[|<->|, thick] (%f, 0.75) -- node[midway, above, font=\\small]{\\SI{%d}{m}} (%f, 0.75);", d_effort, d_load, s),
    sprintf("\\draw[|<->|, thick] (%f, 1.25) -- node[midway, above, font=\\small]{\\SI{%d}{m}} (%f, 1.25);", 0, s, s),
  "\\end{tikzpicture}")
```

Question
========

A lever is \SI{`r d_effort + d_load`}{m} long. The distance from the fulcrum to the load to be lifted is \SI{`r d_load`}{m}. If a worker pushes on the opposite end with \SI{`r f_effort`}{N}, what is the maximum weight that can be lifted?

\vspace{1em}

```{r, echo = FALSE, results = "asis"}
include_tikz(tikz, name = "lever", format = typ, packages="siunitx")
```

```{r, echo = FALSE, results = "asis"}
answerlist(sc$questions, markup = "markdown")
```

Solution
========
The maximum weight that can be moved at constant velocity is the weight that makes a torque equal to the torque generated by the worker.
$$F_{worder} d_{worker} = F_{load} d_{load}$$
Where $d_{worker} = \SI{`r s`}{m} - \SI{`r d_load`}{m} = \SI{`r d_effort`}{m}$. Therefore, solving for $F_{load}$:
$$F_{load} = \frac{d_{worker}}{d_{load}} F_{worker} = \left(\frac{`r d_effort`}{`r d_load`}\right) \SI{`r f_effort`}{N} = \SI{`r signif(max_load, 3)`}{N}$$



Meta-information
================
exname: calculate lever max weight
extype: schoice
exsolution: `r mchoice2string(sc$solutions)`
exshuffle: 4

