```{r, echo = FALSE, results = "hide"}
sep <- sample(1:9, 1) # separation between two scales in metres
plank_mass <- 2 * sample(1:5, 1) # in kg
left_mass <- 10 * sample(2:5, 1) # in kg
right_mass <- 10 * sample(6:9, 1) # in kg

rock_mass <- left_mass + right_mass - plank_mass

ans <- sep / rock_mass * (right_mass - plank_mass / 2)
sc <- num_to_schoice(ans, delta = 0.005, range = c(0.1*ans ,sep), format = FALSE)
sc$questions <- sapply(sc$questions, signif, 3)
sc$questions <- sprintf("$\\SI{%g}{m}$", sc$questions)
```

Question
========
Two scales are separated by \SI{`r fmt(sep, 1)`}{m}, and a plank of mass \SI{`r fmt(plank_mass, 1)`}{kg} is placed between them. Each scale is observed to read \SI{`r fmt(plank_mass/2, 1)`}{kg}. A rock is placed somewhere on the plank, after which the left scale reads \SI{`r fmt(left_mass, 1)`}{kg} and the right scale reads \SI{`r fmt(right_mass, 1)`}{kg}. How far from the left scale was the rock placed?

```{r questionlist, echo = FALSE, results = "asis"}
answerlist(sc$questions, markup = "markdown")
```

Solution
========
The first condition for static equilibrium is that the net force on the plank must be zero. This implies that the mass of the rock is the sum of the two scale readings minus the plank's mass:
$$m_{rock} = \SI{`r left_mass`}{kg} + \SI{`r right_mass`}{kg} - \SI{`r plank_mass`}{kg} = \SI{`r rock_mass`}{kg}$$
The second condition for static equilibrium is that the net torque on the plank must be zero. You can choose any axis to calculate the torque. Let's arbitrarily choose the left scale as the pivot. Also, let $s$ be the separation between the two scales and $x$ be the distance of the rock from the left scale. Then,
$$\frac{s}{2} m_{plank} + x m_{rock} - sm_{right} = 0$$
Solving for $x$, we get:
$$x = \frac{s}{m_{rock}} \left(m_{right} - \frac{m_{plank}}{2} \right) = \frac{\SI{`r sep`}{m}}{\SI{`r rock_mass`}{kg}} \left(\SI{`r right_mass`}{kg} - \frac{\SI{`r plank_mass`}{kg}}{2} \right) = \SI{`r signif(ans, 2)`}{m}$$

Meta-information
================
exname: calculate position of rock between two scales
extype: schoice
exsolution: `r mchoice2string(sc$solutions)`
exshuffle: 4
