```{r, echo = FALSE, results = "hide"}
E <- 9292#sample(1000:9999, 1) # rocket fuel energy (J)
m <- 58#sample(10:99, 1) # mass of rocket (kg)

ans <- E / m / 9.8

sc <- num_to_schoice(ans, delta = ans/10, digits = 5, format = FALSE)
sc$questions <- sprintf("$%g \\mathsf{\\,m}$", signif(sc$questions, 3))
```

Question
========
A test rocket of mass `r m` kg is fired straight up. Its fuel gives it a kinetic
energy of `r E` J by the time the rocket engine burns all the fuel. What additional
height will the rocket rise?

```{r, echo = FALSE, results = "asis"}
answerlist(sc$questions, markup = "markdown")
```


Solution
========
The rocket will rise an additional height such that all of its kinetic energy
is transformed into gravitational potential energy, $E_p = mgh$. 

$$h = \frac{E_p}{mg} = \frac{(`r E` \mathsf{\,J})}{(`r m` \mathsf{\,kg})(9.80 \mathsf{\,m/s^2})}
= `r signif(ans, 3)` \mathsf{\,m}$$


Meta-information
================
exname: Calculate rocket height
extype: schoice
exsolution: `r mchoice2string(sc$solutions)`
exshuffle: 4
