```{r, echo = FALSE, results = "hide"}
options(scipen = 999)
m <- sample(2000:5000, 1) # mass (kg)
h <- sample(10:50, 1) # height (m)
p <- sample(10:30, 1) # power (kW)

ans <- m * 9.8 * h / p / 1000 # time (s)

sc <- num_to_schoice(ans, delta = ans/10, format = FALSE)
sc$questions <- sprintf("$%g \\mathsf{\\,s}$", signif(sc$questions, 3))
```

Question
========
An electric motor develops `r fmt(p,1)` kW of power as it lifts a loaded elevator up a
distance of `r fmt(h,1)` m. The total mass of the elevator and passengers is `r m` kg. 
How long does the elevator take to complete complete this trip?

```{r, echo = FALSE, results = "asis"}
answerlist(sc$questions, markup = "markdown")
```


Solution
========
Power is work over time, so time is work over power:
$$t = \frac{W}{P} = \frac{Fd}{P} = \frac{mgh}{P} = \frac{(`r fmt(m,1)` \mathsf{\,kg})(9.80 \mathsf{\,N/kg})(`r fmt(h, 1)` \mathsf{\,m})}{`r p * 1000` \mathsf{\,W}} = `r signif(ans, 3)` \mathsf{\,s}$$


Meta-information
================
exname: Calculate time given power of elevator
extype: schoice
exsolution: `r mchoice2string(sc$solutions)`
exshuffle: 4
