```{r, echo = FALSE, results = "hide"}
options(scipen=999)
d <- sample(1:20, 1) # distance (m)
a <- sample(20:60, 1) # angle (deg)
f <- sample(100:999, 1) # pulling force (N)
mu <- signif(runif(1, 0.1, 1), 2) # coefficient of friction -- not used
m <- sample(10:99, 1) # mass of box (kg) -- not used

ans <- f * d * cos(a * pi / 180) # work (J)
dis <- c(f * d)

sc <- num_to_schoice(ans, wrong = dis, delta = ans/100, format = FALSE)
sc$questions <- sprintf("$%g \\mathsf{\\,J}$", signif(sc$questions, 3))
```

Question
========
A rope is used to pull a box $`r fmt(d, 1)` \mathsf{\,m}$ across the floor. The rope is held at
an angle of $`r fmt(a, 1)`^\circ$ with the floor and a force of $`r f` \mathsf{\,N}$ is used.
The mass of the box is $`r m` \mathsf{\,kg}$ and the coefficient of kinetic 
friction  between the box and the ground is $`r mu`$.
How much work does the force on the rope do?

```{r, echo = FALSE, results = "asis"}
answerlist(sc$questions, markup = "markdown")
```


Solution
========
Work is the component of force in the direction of motion times the distance.
The coefficient of kinetic friction and the mass of the box are not needed 
because the question asks for the work done by the force on the rope and not the
work done by friction.

$$W = Fd \cos\theta = (`r f` \mathsf{\,N})(`r fmt(d, 1)` \mathsf{\,m})\cos(`r fmt(a, 1)`^\circ) = `r signif(ans, 3)` \mathsf{\,J}$$


Meta-information
================
exname: Calculate work done pulling at angle
extype: schoice
exsolution: `r mchoice2string(sc$solutions)`
exshuffle: 4
