```{r, echo = FALSE, results = "hide"}
m <- sample(1000:2000, 1) # mass of car (kg)
v <- sample(10:30, 1) # speed (m/s)
f <- sample(1000:9999, 1) # braking force (N)

ans <- 0.5 * m * v^2 / f

sc <- num_to_schoice(ans, delta = ans / 10, format = FALSE)
sc$questions <- sprintf("%.1f m", signif(sc$questions, 3))
```
Question
========
A `r m`-kg car is traveling at `r v` m/s. The brakes are suddenly applied and the
car slides to a stop. The average braking force between the tires and the road
is `r f` N. How far will the car slide once the brakes are applied?

```{r, echo = FALSE, results = "asis"}
answerlist(sc$questions, markup = "markdown")
```


Solution
========
The work done by the brakes equals the kinetic energy of the car.

$$W = Fd = \frac{1}{2}mv^2$$
Therefore, solving for $d$,

$$d = \frac{m}{2Fv^2} = `r signif(ans, 3)` \mathsf{\,m}$$


Meta-information
================
exname: Calculate braking distance
extype: schoice
exsolution: `r mchoice2string(sc$solutions)`
exshuffle: 4
