```{r, echo = FALSE, results = "hide"}
angle <- sample(10:80, 1) # (deg)

ans <- 1 / sin(angle * pi / 180) # IMA

sc <- num_to_schoice(ans, delta = ans/10, format = FALSE)
sc$questions <- sprintf("%.3f", signif(sc$questions, 3))
```

Question
========
A box is pushed up an inclined plane. The angle of incline is $`r angle`^\circ$ 
from the ground. What is the ideal mechanical advantage of the inclined plane?

```{r, echo = FALSE, results = "asis"}
answerlist(sc$questions, markup = "markdown")
```


Solution
========
The ideal mechanical advantage is the effort distance over the resistance distance.
The effort distance is the along the inclined surface, which is the hypotenuse of
the right triangle. The resistance distance is the vertical distance, which is the
side opposite the angle.

$$IMA = \frac{d_e}{d_r} = \frac{\mathsf{hypotenuse}}{\mathsf{opposite}}
= \frac{1}{\sin(`r angle`^\circ)} = `r fmt(ans,3)`$$


Meta-information
================
exname: Calculate IMA of inclined plane
extype: schoice
exsolution: `r mchoice2string(sc$solutions)`
exshuffle: 4
