```{r, echo = FALSE, results = "hide"}
v <- sample(10:120, 2) # speeds (km/h)
d <- sample(10: 100, 1) # braking distance (m)

ans <- d * (v[2] / v[1]) ^ 2

sc <- num_to_schoice(ans, delta = ans/10, format = FALSE)
sc$questions <- sprintf("$%.1f \\mathsf{\\,m}$", sc$questions)
```

Question
========
A car moving at `r v[1]` km/h comes to a stop in `r d` m after the driver applies the brakes.
How far would the same car take to stop if it were moving at `r v[2]` km/h? 
Assume identical road conditions and braking force.

```{r, echo = FALSE, results = "asis"}
answerlist(sc$questions, markup = "markdown")
```


Solution
========
The braking force does work to remove the kinetic energy of the car. Since kinetic
energy depends on velocity squared, the car has 
$(`r v[2]` / `r v[1]`)^2 = `r (v[2] / v[1]) ^ 2`$ times the kinetic energy when it
is traveling at $`r v[2]`$ km/h than when it is traveling at $`r v[1]`$ km/h. 
The work done by the brakes must also be multiplied by $(`r v[2]` / `r v[1]`) ^ 2$.

Since $W=Fd$ and we are assuming the same braking force, the distance
must be multiplied by $(`r v[2]` / `r v[1]`) ^ 2$.

$$d = (`r v[2]` / `r v[1]`) ^ 2 (`r d` \mathsf{\,m}) = `r fmt(ans, 1)` \mathsf{\,m}$$


Meta-information
================
exname: Proportional reasoning - braking distance
extype: schoice
exsolution: `r mchoice2string(sc$solutions)`
exshuffle: 4
