```{r, echo = FALSE, results = "hide"}
v <- sample(1200:1500, 1) # speed of sound in water (m/s)
t <- signif(runif(1, 0.01, 1), 3)
  
ans <- signif(v * t / 2, 3) # freq (Hz)
dis <- c(v * t)

sc <- num_to_schoice(ans, wrong = dis, delta = ans/10, format = FALSE, digits = 6)
sc$questions <- sprintf("$%g \\,\\mathsf{m}$", signif(sc$questions, 3))
```
Question
========
A sonar signal (sound wave) is emitted from a submarine and returns $`r t` \,\mathsf{s}$ later. The speed of sound in water is $`r v` \,\mathsf{m/s}$. 
How far away is the object that reflected the sonar signal?

```{r, echo = FALSE, results = "asis"}
answerlist(sc$questions, markup = "markdown")
```

Solution
========
The distance to the object is half the distance traveled by the sonar signal
because the sonar had to go there and back.

$$ d = v t / 2 = (`r v` \,\mathsf{m/s}) (`r t` \,\mathsf{s}) / 2 = `r ans` \,\mathsf{m} $$


Meta-information
================
exname: Calculate distance using sonar
extype: schoice
exsolution: `r mchoice2string(sc$solutions)`
exshuffle: 4

