```{r, echo = FALSE, results = "hide"}
harmonic <- sample(1:5, 1) # harmonic number
freq <- sample(20:2000, 1) # frequency (Hz)
string_len <- signif(runif(1, 0.2, 2), 3) # (m)

wavelength <- 2 * string_len / harmonic
ans <- signif(freq * wavelength, 3) # speed (m/s)

sc <- num_to_schoice(ans, delta = ans/10, format = FALSE, digits = 6)
sc$questions <- sprintf("$%g \\,\\mathsf{m/s}$", signif(sc$questions, 3))
```
Question
========
The distance between the two fixed ends of a piece of string is $`r string_len` \,\mathsf{m}$.
When the string is vibrating at harmonic number `r harmonic`, the frequency is $`r freq` \,\mathsf{Hz}$.
What is the speed of the waves on the string?

```{r, echo = FALSE, results = "asis"}
answerlist(sc$questions, markup = "markdown")
```

Solution
========
The wavelength is

$$ \lambda = \frac{2 L}{n} = `r wavelength` \,\mathsf{m}$$
The speed is the wavelength times the frequency.

$$ v = f \lambda = (`r freq` \,\mathsf{Hz}) (`r wavelength` \,\mathsf{m}) = `r ans` \,\mathsf{m/s}$$


Meta-information
================
exname: Calculate speed given harmonic and frequency
extype: schoice
exsolution: `r mchoice2string(sc$solutions)`
exshuffle: 4

