```{r, echo = FALSE, results = "hide"}
f_source <- sample(400:500, 1) # car horn freq (Hz)
v_source <- sample(1:30, 1) # m/s
v_sound <- sample(330:360, 1) # m/s

ans <- f_source / (1 + v_source / v_sound)

sc <- num_to_schoice(ans, delta = ans/10, format = FALSE, digits = 6)
sc$questions <- sprintf("%.0f Hz", signif(sc$questions, 3))
```

Question
========
A car horn emits a frequency of `r f_source` Hz when the car is stationary. If the speed of sound in air is `r v_sound` m/s, what frequency will an observer hear as the car is
receding at a speed of `r v_source` m/s while the horn is sounding?

```{r, echo = FALSE, results = "asis"}
answerlist(sc$questions, markup = "markdown")
```

Solution
========
The doppler shifted frequency for a receding source is

$$ f_{obs} = \frac{f_{source}}{1 + v_{source} / v_{sound}} = `r fmt(ans, 0)` \,\mathsf{Hz} $$


Meta-information
================
exname: Calculate Doppler Frequency Receding Source
extype: schoice
exsolution: `r mchoice2string(sc$solutions)`
exshuffle: 4

