```{r, echo = FALSE, results = "hide"}
L <- signif(runif(1, 0.2, 2), 1) # m

int_names <- c("unison", "major second", "major third", "perfect fourth", "perfect fifth", 
             "major sixth", "major seventh", "octave")
int_ratios <- c(1, 9/8, 5/4, 4/3, 3/2, 5/3, 15/8, 2)
i <- sample(2:8, 1)
  
ans <- signif(L / int_ratios[i], 3)

sc <- num_to_schoice(ans, delta = ans/10, format = FALSE, digits = 6)
sc$questions <- sprintf("%g m", signif(sc$questions, 3))
```
Question
========
One organ pipe has a length of `r fmt(L,1)` m. A second pipe should have a pitch one
`r int_names[i]` higher. The pipe should be how long?

```{r, echo = FALSE, results = "asis"}
answerlist(sc$questions, markup = "markdown")
```

Solution
========
The speed is the same in both pipes and both resonate at their fundamental frequency. Therefore,
frequency and wavelength are inversely proportional to each other. 
In order for the second pipe to play a higher sound, it must have a shorter length.

$$ L = (`r L` \,\mathsf{m}) / (`r int_ratios[i]`) = `r ans` \,\mathsf{m} $$


Meta-information
================
exname: Calculate pipe length given interval
extype: schoice
exsolution: `r mchoice2string(sc$solutions)`
exshuffle: 4

