```{r, echo = FALSE, results = "hide"}
r <- signif(runif(1, 1.5, 30), 3) # years
ans <- r ^ (3 / 2) # au

sc <- num_to_schoice(ans, delta = ans/10, format = FALSE)
sc$questions <- sprintf("%.1f years", sc$questions)
```
Question
========
An asteroid orbits the sun at an average distance of `r r` au. What is the 
period of the asteroid's orbit? Note: One astronomical unit (au) is the average
distance from the earth to the sun.

```{r, echo = FALSE, results = "asis"}
answerlist(sc$questions, markup = "markdown")
```

Solution
========
Kepler's Third Law of Planetary Motion states that the square of the orbital
period is proportional to the cube of the average distance
$$\left( \frac{T_{asteroid}}{T_{earth}} \right)^2 = \left( \frac{R_{asteroid}}{R_{earth}} \right)^3$$
We are given that $R_{asteroid} / R_{earth} = `r r`$ and $T_{earth} = 1$ year. Therefore,
$$R_{asteroid} = \sqrt{(`r r`)^3} \text{ years} = `r fmt(ans, 1)` \text{ years}$$


Meta-information
================
exname: Calculate r given t (kepler's law)
extype: schoice
exsolution: `r mchoice2string(sc$solutions)`
exshuffle: 4

