```{r, echo = FALSE, results = "hide"}
M <- 5.97e24 # mass of earth (kg)
R <- 6.38e6 # radius of earth (m)
G <- 6.67e-11

h <- sample(200:2000, 1) # altitude of orbit (km)
m <- sample(100:1000, 1) # mass of satellite (kg)

ans <- G*M*m * (1/R - 1/(2*(R+h*1000))) / 1e9 # energy (GJ)

sc <- num_to_schoice(ans, delta = ans/50, format = FALSE)
sc$questions <- sprintf("%.1f GJ", sc$questions)
```
Question
========
A `r m`-kg satellite is in a circular orbit at an altitude of `r h` km around the earth.
How much energy (kinetic and potential) would it release if it were to crash down
onto the surface of the earth?

```{r, echo = FALSE, results = "asis"}
answerlist(sc$questions, markup = "markdown")
```

Solution
========
During the crash, the satellite would lose its kinetic energy and some of its
potential energy.
$$\Delta E = GMm \left(\frac{1}{R} - \frac{1}{2(R+h)} \right) = `r fmt(ans,1)` \text{ GJ}$$


Meta-information
================
exname: Calculate Crash Energy
extype: schoice
exsolution: `r mchoice2string(sc$solutions)`
exshuffle: 4

