```{r, echo = FALSE, results = "hide"}
q <- sample(c(-9:-2, 2:9), 2) # two charges (microcoulombs)
s <- sample(2:9, 1) # side length of square (m)

ans <- 9e9 / s^2 * sqrt(sum((q * 1e-6)^2)) # N/C

sc <- num_to_schoice(ans, delta = ans/10, format = FALSE, digits = 5)
sc$questions <- sprintf("$%g \\,\\mathsf{N/C}$", signif(sc$questions, 2))

# use the same graphics type (pdf, svg, png) as the current xweave() call
typ <- match_exams_device()

## tikz graphic
tikz <- c("\\begin{tikzpicture}",
  "\\draw[dashed] (0,0) -- (0,2) -- (2,2) -- (2,0) -- cycle;",
  "\\filldraw[fill=black] (0,2) circle (2pt) node[anchor=east]{$q_1$};",
  "\\filldraw[fill=black] (2,0) circle (2pt) node[anchor=west]{$q_2$};",
  "\\filldraw[fill=black] (2,2) circle (2pt) node[anchor=west]{$P$};",
  "\\end{tikzpicture}")
```

Question
========
Two point charges, $q_1 = `r fmt(q[1],1)`\,\mu\mathsf{C}$ and $q_2 = `r fmt(q[2],1)`\,\mu\mathsf{C}$,
are fixed at opposing corners of a square of side length $`r fmt(s,1)`\,\mathsf{m}$
as shown in the figure. What is the electric field strength at one of the 
unoccupied corners of the square (point $P$ in the figure)?

```{r, echo = FALSE, results = "asis"}
include_tikz(tikz, name = "charges-in-square", format = typ)
```

```{r, echo = FALSE, results = "asis"}
answerlist(sc$questions, markup = "markdown")
```


Solution
========
At point $P$, the electric field from $q_1$ will be at a right angle to the 
electric field from $q_2$. Therefore, the net electric field strength can be
calculated using the Pythagorean theorem.

$$E = \sqrt{E_1^2 + E_2^2} = \frac{k}{s^2} \sqrt{q_1^2 + q_2^2} = `r signif(ans,2)`\,\mathsf{N/C}$$

Meta-information
================
exname: Calculate electric field opposing corners of square
extype: schoice
exsolution: `r mchoice2string(sc$solutions)`
exshuffle: 4
