```{r, echo = FALSE, results = "hide"}
E <- sample(10:99, 1) # (N/C)
V0 <- sample(100:999, 1) # (V)
d <- sample(1:9, 1) # (m)

s <- sample(-1:1, 1) # sign
directions <- c("east", "south", "west") # in order based on s

ans <- signif(V0 + E * d * s, 3)  # voltage

sc <- num_to_schoice(ans, delta = ans/10, range = c(-2, 2) * ans, format = FALSE)
sc$questions <- sprintf("%g V", signif(sc$questions, 3))
```
Question
========
Consider a uniform electric field of $`r fmt(E,1)` \,\mathsf{N/C}$ pointing
toward the east. If the voltage measured relative to ground at a given point in the
field is $`r V0` \,\mathsf{V}$, what is the voltage $`r fmt(d,2)` \,\mathsf{m}$
directly `r directions[s + 2]` of the point?

```{r, echo = FALSE, results = "asis"}
answerlist(sc$questions, markup = "markdown")
```

Solution
========
The voltage changes with distance in a uniform electric field following the formula

$$V = Ed$$

The potential decreases moving in the same direction as the electric field and increases
moving in the opposite direction. When moving perpendicular to the electric field,
the potential does not change. Therefore, for this question, the voltage is

$$V = `r V0` \,\mathsf{V} + (`r s * d`\,\mathsf{m})(`r E` \,\mathsf{N/C}) = `r ans`\,\mathsf{V}$$


Meta-information
================
exname: Calculate voltage moving in uniform electric field
extype: schoice
exsolution: `r mchoice2string(sc$solutions)`
exshuffle: 4

