```{r, echo = FALSE, results = "hide"}
options(scipen = 999)
R <- signif(runif(1, 5, 15), 2) # resistance (ohms)
V <- sample(110:120, 1) # voltage (V)
t <- signif(runif(1, 2, 12), 2) # time (h)

ans <- signif(V^2 / R * t / 1000, 2)

sc <- num_to_schoice(ans, delta = ans/10, format = FALSE, digits = 5)
sc$questions <- sprintf("$%g \\,\\mathsf{kWh}$", signif(sc$questions, 2))
```
Question
========
A space heater with a resistance of  $`r R` \,\mathsf{\Omega}$ operates at a 
voltage of $`r V` \,\mathsf{V}$. How much energy does the space heater use in 
$`r t` \,\mathsf{hours}$?

```{r, echo = FALSE, results = "asis"}
answerlist(sc$questions, markup = "markdown")
```

Solution
========
Find the power of the device using $P = IV = V^2 / R$ and multiply by the time. Remember to convert all units.
$$E = P t = \frac{V^2}{R} t = \frac{(`r V` \,\mathsf{V})^2}{`r R` \,\mathsf{\Omega}}(`r t` \,\mathsf{h}) = `r ans*1000` \,\mathsf{Wh} = `r ans` \,\mathsf{kWh}$$


Meta-information
================
exname: Calculate energy given I V t
extype: schoice
exsolution: `r mchoice2string(sc$solutions)`
exshuffle: 4

