```{r, echo = FALSE, results = "hide"}
R <- sample(100:999, 1) # resistance (ohms)
n <- sample(100:999, 1) # number of resistors in parallel

ans <- R / n

sc <- num_to_schoice(ans, delta = ans/10, format = FALSE, digits = 5)
sc$questions <- sprintf("$%g \\,\\mathsf{\\Omega}$", signif(sc$questions, 2))
```
Question
========
A total of `r n` resistors, all with resistance $`r R` \,\mathsf{\Omega}$, 
are connected in **parallel**. What is the equivalent resistance of the resistors?

```{r, echo = FALSE, results = "asis"}
answerlist(sc$questions, markup = "markdown")
```

Solution
========
The equivalent resistance of resistors in parallel when they all have the same resistance $R_i$ is 

$$R = \left( \frac{1}{R_i} + \frac{1}{R_i} + \frac{1}{R_i} + ... \right)^{-1} = \frac{R_i}{`r n`} = `r signif(ans, 2)` \,\mathsf{\Omega}$$


Meta-information
================
exname: Calculate resistance of 100 resistors in parallel
extype: schoice
exsolution: `r mchoice2string(sc$solutions)`
exshuffle: 4

