```{r, echo = FALSE, results = "hide"}
I <- signif(runif(1, 100, 300), 2) # current (mA)
V <- signif(runif(1, 3, 5), 2) # voltage (V)
t <- signif(runif(1, 2, 10), 2) # time (min)

P <- I / 1000 * V # power (W)

ans <- signif(P * t * 60, 2)
dis <- c(I * V * t, I / 1000 * V * t)

sc <- num_to_schoice(ans, wrong = dis, range = c(0.5, 2)*ans, delta = ans/10, format = FALSE, digits = 5)
sc$questions <- sprintf("$%g \\,\\mathsf{J}$", signif(sc$questions, 2))
```
Question
========
An electronic device is powered by a $`r V` \,\mathsf{V}$ battery. The current used
to operate the device is $`r I` \,\mathsf{mA}$. How much energy does the device
use in $`r t` \,\mathsf{minutes}$?

```{r, echo = FALSE, results = "asis"}
answerlist(sc$questions, markup = "markdown")
```

Solution
========
Find the power of the device using $P = IV$ and multiply by the time. Remember to convert all units.
$$E = P t = I V t = (`r I/1000` \,\mathsf{A})(`r V` \,\mathsf{V})(`r t` \times 60 \,\mathsf{s}) = `r ans` \,\mathsf{J}$$


Meta-information
================
exname: Calculate energy given I V t
extype: schoice
exsolution: `r mchoice2string(sc$solutions)`
exshuffle: 4

