```{r, echo = FALSE, results = "hide"}
R <- sample(10:99, 2) # resistance (ohms)
I <- signif(runif(1, 100, 1000), 1) # current (A)

ans <- (R[2] / sum(R)) * I

sc <- num_to_schoice(ans, range = c(0.5, 2)*ans, delta = ans/10, format = FALSE, digits = 5)
sc$questions <- sprintf("$%g \\,\\mathsf{mA}$", signif(sc$questions, 2))
```
Question
========
A $`r I` \,\mathsf{mA}$ current flows into a parallel combination of a 
$`r R[1]` \,\mathsf{\Omega}$ and a $`r R[2]` \,\mathsf{\Omega}$ resistor. What 
current flows through the $`r R[1]` \,\mathsf{\Omega}$ resistor?

```{r, echo = FALSE, results = "asis"}
answerlist(sc$questions, markup = "markdown")
```

Solution
========
The total current is equal to the sum of the current through each resistor

$$I = I_1 + I_2$$
The voltage across each resistor is the same and $V = IR$ so

$$I_1 R_1 = I_2 R_2$$
Combining the two equations and solving for $I_1$ gives

$$I_1 = \left(\frac{R_2}{R_1 + R_2}\right)I = `r signif(ans, 2)` \,\mathsf{mA}$$


Meta-information
================
exname: Calculate current in parallel resistor given total current
extype: schoice
exsolution: `r mchoice2string(sc$solutions)`
exshuffle: 4

