```{r, echo = FALSE, results = "hide"}
m <- sample(10:99, 1) # mass (g)
h <- sample(1:20, 1) # height (m)
p <- (m/1000) * sqrt(2 * 9.8 * h) # momentum (kg m/s)

distractors <- c(m * h, p * 1000)
sc <- num_to_schoice(p, wrong = distractors, delta = p/10, format = FALSE)
sc$questions <- signif(sc$questions, 2)
sc$questions <- sprintf("\\SI{%g}{kg.m/s}", sc$questions)
```

Question
========
A ball of mass \SI{`r m`}{g} is dropped from a height of \SI{`r h`}{m}. Its
momentum just before it strikes the ground is

```{r, echo = FALSE, results = "asis"}
answerlist(sc$questions, markup = "markdown")
```


Solution
========
The velocity of the ball just before hitting the ground can be calculated using
conservation of mechanical energy

$$\frac{1}{2} m v^2 = mgh$$
$$v = \sqrt{2gh}$$

The momentum is the product of mass and velocity
$$
p = m v = m\sqrt{2gh} = (\SI{`r m/1000`}{kg})\sqrt{2(\SI{9.8}{m/s^2})(\SI{`r h`}{m})} = \SI{`r signif(p, 2)`}{kg.m/s}
$$


Meta-information
================
exname: Calculate Momentum of Dropped Ball
extype: schoice
exsolution: `r mchoice2string(sc$solutions)`
exshuffle: 4
