```{r, echo = FALSE, results = "hide"}
m <- signif(runif(1, 1, 9), 2) # mass of ball (kg)
v <- sort(sample(10:30, 2), decreasing = TRUE) # speed (m/s)
t <- signif(runif(1, 0.1, 1), 2) # contact time (ms)

ans <- signif(m * sqrt(sum(v^2)), 2)
dis <- c(v[1] - v[2], m * sqrt(v[1]^2 - v[2]^2))
sc <- num_to_schoice(ans, delta = ans/10, format = FALSE)
sc$questions <- sprintf("$%g \\,\\mathsf{N\\,s}$", signif(sc$questions, 2))
```

Question
========
A $`r m` \,\mathsf{kg}$ object moving due north at $`r v[1]` \,\mathsf{m/s}$ collides with a barrier for $`r t` \,\mathsf{s}$, resulting in a final velocity of $`r v[2]` \,\mathsf{m/s}$ due east. What is the magnitude of impulse on the object?

```{r questionlist, echo = FALSE, results = "asis"}
answerlist(sc$questions, markup = "markdown")
```

Solution
========
The impulse is equal to the change in momentum, which is a vector quantity.

$$\Delta \vec{p} = \vec{p_f} - \vec{p_i} = \vec{p_f} + (-\vec{p_i})$$

It is thus the sum of two perpendicular vectors, $\vec{p}_f$ which points east, and $-\vec{p}_i$ which points south. The magnitude of impulse can be calculated using the Pythagorean theorem.

$$\mathsf{impulse} = m\sqrt{v_f^2 + v_i^2} = (`r m` \,\mathsf{kg}) \sqrt{(`r v[1]` \,\mathsf{m/s})^2 + (`r v[2]` \,\mathsf{m/s})^2} = `r ans` \,\mathsf{N\, s}$$


Meta-information
================
exname: Calculate Impulse Right Angle Collision
extype: schoice
exsolution: `r mchoice2string(sc$solutions)`
exshuffle: 4
