```{r, echo = FALSE, results = "hide"}
f <- sample(500:1500, 1) # force to knock down door (N)
r <- sample(10:40, 1) # rate of water flow (kg / s)
v <- f / r # velocity of water needed (m / s)

sc <- num_to_schoice(v, range = c(v / 2, 2 * v), delta = v / 10, format = FALSE)
sc$questions <- signif(sc$questions, 2)
sc$questions <- sprintf("%g m/s", sc$questions)
```

Question
========
A fire hose is turned on the door of a burning building in order to knock it down.
This requires a force of $`r f`$ N. If the hose delivers $`r r`$ kg / s, what is the velocity of water
needed, assuming that the water doesn't bounce back?

```{r, echo = FALSE, results = "asis"}
answerlist(sc$questions, markup = "markdown")
```


Solution
========
The impulse is related to the momentum by
$$
F \Delta t = m \Delta v
$$
Since the water does not bounce back, $v_f = 0$ and $\Delta v = -v_i$, where $v_i$
is the velocity of the water needed to knock down the door. Therefore,
$$v_i = F \left( \frac{\Delta t}{m} \right) = (`r f` \text{ N}) / (`r r`\text{ kg / s}) = `r signif(v, 2)` \text{ m/s}$$


Meta-information
================
exname: Calculate Velocity of Water From Fire Hose
extype: schoice
exsolution: `r mchoice2string(sc$solutions)`
exshuffle: 4
