```{r, echo = FALSE, results = "hide"}
options(scipen = 999)
m <- sample(100:200, 1) # mass of ball (g)
v <- sample(10:40, 1) # initial speed (m/s)
t <- signif(runif(1, 1, 2), 2) # contact time (ms)

f <- 2 * m * v / t
distractors <- c(1000*f, f/1000, f/2)

sc <- num_to_schoice(f, wrong = distractors, delta = f/100, format = FALSE)

sc$questions <- signif(sc$questions, 3)
sc$questions <- sprintf("\\SI{%g}{N}", sc$questions)
```

Question
========
A `r m` g baseball is thrown towards a batter at `r v` m/s. The batter hits the
ball back along the same path, and at the same speed. If the bat was in contact
with the ball for `r t` ms, the average force exerted by the bat was

```{r questionlist, echo = FALSE, results = "asis"}
answerlist(sc$questions, markup = "markdown")
```

Solution
========
The impulse is equal to the change in momentum

$$F \Delta t = m \Delta v$$
Solving for $F$

$$F = \frac{m \Delta v}{\Delta t} = \frac{(\SI{`r m/1000`}{kg})(\SI{`r v`}{m/s} - \SI{`r -v`}{m/s})}{\SI{`r t/1000`}{s}} = \SI{`r signif(f,3)`}{N}$$

Meta-information
================
exname: calculate average force baseball bat
extype: schoice
exsolution: `r mchoice2string(sc$solutions)`
exshuffle: 4
