```{r, echo = FALSE, results = "hide"}
m <- sample(10:99, 1) # bullet mass (g)
M <- sample(1:10, 1) # block mass (kg)
h <- sample(10:99, 1) # height of swing (cm)

v <- (m/1000 + M) / (m/1000) * sqrt(2 * 9.8 * h/100)

sc <- num_to_schoice(v, range = c(v / 2, 2 * v), delta = v / 10, format = FALSE)
sc$questions <- signif(sc$questions, 3)
sc$questions <- sprintf("%g m/s", sc$questions)
```

Question
========
A bullet (`r m` g) is fired into the wooden block ($`r fmt(M, 2)`$ kg) of a ballistic pendulum. As a result, the
bullet is lodged into the block, and the centre of mass of the pendulum-projectile system swings up to
a maximum height of $`r h`$ cm. What was the initial speed of the bullet? 

```{r, echo = FALSE, results = "asis"}
answerlist(sc$questions, markup = "markdown")
```


Solution
========
Conservation of momentum for the initial inelastic collision gives
$$m v_1 = (m + M) v'$$
The maximum pendulum swing height can be calculated using conservation of
energy during the swing.
$$v' = \sqrt{2gh}$$
The speed of the bullet can be found by combining the two equations
$$v_1 = \frac{m + M}{m} \sqrt{2gh} = \frac{`r m/1000` + `r M`}{`r m/1000`} \sqrt{2(\SI{9.8}{m/s^2})(\SI{`r h/100`}{m})} = \SI{`r signif(v, 3)`}{m/s}$$


Meta-information
================
exname: Calculate Bullet Speed Ballistic Pendulum
extype: schoice
exsolution: `r mchoice2string(sc$solutions)`
exshuffle: 4
