```{r, echo = FALSE, results = "hide"}
options(scipen = 999)
M <- sample(5:15, 1) # mass of machine gun (kg)
m <- sample(10:50, 1) # mass of bullets (g)
v <- sample(600:1200, 1) # muzzle speed (m/s)
rpm <- sample(600:1500, 1) # rounds per minute

f <- (m / 1000) * v * (rpm / 60)
distractors <- c(f * 60, f * 1000)

sc <- num_to_schoice(f, wrong = distractors, delta = f/100, format = FALSE)

sc$questions <- sprintf("%g N", signif(sc$questions, 3))
```

Question
========
A machine gun, of mass $`r M`$ kg, fires bullets of mass $`r m`$ g, with a muzzle speed of
$`r v`$ m/s, at the rate of $`r rpm`$ rounds per minute. What is the average force exerted
on the machine gun mount?

```{r questionlist, echo = FALSE, results = "asis"}
answerlist(sc$questions, markup = "markdown")
```

Solution
========
The impulse is equal to the change in momentum

$$F \Delta t = m \Delta v$$
Solving for $F$

$$F = \frac{m \Delta v}{\Delta t} = (\SI{`r m/1000`}{kg})(\SI{`r v`}{m/s})(\SI{`r rpm`}{rpm})(1/(\SI{60}{s/min})) = \SI{`r signif(f, 3)`}{N}$$

Meta-information
================
exname: Calculate Average Force on Machine Gun Mount
extype: schoice
exsolution: `r mchoice2string(sc$solutions)`
exshuffle: 4
