```{r, echo = FALSE, results = "hide"}
v <- signif(runif(1, 1, 2.9), 3) # x 10^8 m/s
L0 <- sample(50:100, 1) # contracted length (m)
g <- 1 / sqrt(1 - (v / 3)^2)

ans <- L0 / g
dis <- c(L0 * g)

sc <- num_to_schoice(ans, wrong = dis, range = c(0, 2) * ans, delta = ans/100, format = FALSE, digits = 6)
sc$questions <- sprintf("$%.1f \\,\\mathsf{ly}$", signif(sc$questions, 3))
```

Question
========
If you were to travel to a star $`r fmt(L0, 1)`$ light-years from Earth at a speed of $`r fmt(v, 3)` \times 10^8 \,\mathsf{m/s}$, what would you measure this distance to be?

```{r, echo = FALSE, results = "asis"}
answerlist(sc$questions, markup = "markdown")
```

Solution
========
The distance is contracted in your frame, so it would be shorter than when the Earth and star are at rest.

The Lorentz factor is

$$ \gamma = \frac{1}{\sqrt{1 - v^2 / c^2}} = `r fmt(g, 3)` $$
Therefore, the contracted distance to the star is

$$ L = \frac{L_0}{\gamma} = \frac{`r L0` \,\mathsf{ly}}{`r g`} = `r fmt(ans, 1)` \,\mathsf{ly} $$


Meta-information
================
exname: Calculate Contracted Length
extype: schoice
exsolution: `r mchoice2string(sc$solutions)`
exshuffle: 4

