```{r, echo = FALSE, results = "hide"}
v <- signif(runif(1, 0.1, 0.9), 2)
t <- sample(10:60, 1) # time (s)
g <- 1 / sqrt(1 - v^2)

ans <- g * t
dis <- c(t / g, t * v)

sc <- num_to_schoice(ans, wrong = dis, range = c(0, 10) * ans, delta = ans/100, format = FALSE, digits = 6)
sc$questions <- sprintf("$%.1f \\,\\mathsf{s}$", signif(sc$questions, 3))
```

Question
========
A clock moving at $v = `r fmt(v, 3)` c$ passes your clock when both clocks read $t = 0$. When the moving clock reads $t = `r fmt(t,1)` \,\mathsf{s}$, what do the clocks in your frame read? 

```{r, echo = FALSE, results = "asis"}
answerlist(sc$questions, markup = "markdown")
```

Solution
========
Time is dilated in your frame, so the clocks in your frame would read a greater time interval.

The Lorentz factor is

$$ \gamma = \frac{1}{\sqrt{1 - v^2 / c^2}} = \frac{1}{\sqrt{1 - `r v`^2}} = `r fmt(g, 3)` $$
The clocks in your frame read

$$ \Delta t = \gamma \Delta t_0 = (`r g`)(`r t` \,\mathsf{s}) = `r fmt(ans, 1)` \,\mathsf{s} $$


Meta-information
================
exname: Calculate Dilated Time
extype: schoice
exsolution: `r mchoice2string(sc$solutions)`
exshuffle: 4

