```{r, echo = FALSE, results = "hide"}
v <- signif(runif(1, 0.1, 0.9), 2)
L <- sample(50:100, 1) # contracted length (m)
g <- 1 / sqrt(1 - v^2)

ans <- L * g
dis <- c(L / g)

sc <- num_to_schoice(ans, wrong = dis, range = c(0, 2) * ans, delta = ans/100, format = FALSE, digits = 6)
sc$questions <- sprintf("$%.1f \\,\\mathsf{m}$", sc$questions)
```

Question
========
A rod passes by you at a speed of $`r fmt(v, 3)` c$. You measure its length to be $`r fmt(L, 1)` \,\mathsf{m}$. How long would it be at rest?

```{r, echo = FALSE, results = "asis"}
answerlist(sc$questions, markup = "markdown")
```

Solution
========
The length of the rod is contracted in your frame, so it would be longer when at rest.

The Lorentz factor is

$$ \gamma = \frac{1}{\sqrt{1 - v^2 / c^2}} = \frac{1}{\sqrt{1 - `r v`^2}} = `r fmt(g, 3)` $$
Therefore, the proper length of the rod is

$$ L_0 = \gamma L = (`r g`)(`r L` \,\mathsf{m}) = `r fmt(ans, 1)` \,\mathsf{m} $$


Meta-information
================
exname: Calculate Proper Length
extype: schoice
exsolution: `r mchoice2string(sc$solutions)`
exshuffle: 4

