```{r, echo = FALSE, results = "hide"}
v <- signif(runif(1, 0.1, 0.9), 3)
t <- signif(runif(1, 1, 9.99), 3) # time (10^(-8) s)

ans <- 3 * t

sc <- num_to_schoice(ans, range = c(0, 10) * ans, delta = ans/100, format = FALSE, digits = 6)
sc$questions <- sprintf("$%.1f \\,\\mathsf{m}$", signif(sc$questions, 3))
```

Question
========
A car moving at $v = `r fmt(v, 3)` c$ turns on its headlights. In the car's reference frame, 
what distance does the light cover in $`r fmt(t, 2)` \times 10^{-8} \,\mathsf{s}$? 

```{r, echo = FALSE, results = "asis"}
answerlist(sc$questions, markup = "markdown")
```

Solution
========
The speed of light in any frame is $3.00 \times 10^8 \,\mathsf{m/s}$. Therefore the distance the light traveled is

$$ d = (3.00 \times 10^8 \,\mathsf{m/s})(`r t` \times 10^{-8} \,\mathsf{s}) = `r fmt(ans, 1)` \,\mathsf{m} $$

Meta-information
================
exname: Calculate light distance given time
extype: schoice
exsolution: `r mchoice2string(sc$solutions)`
exshuffle: 4

