```{r, echo = FALSE, results = "hide"}
w <- sample(100:999, 1) # weight (N)
a <- sample(20:60, 1) # angle (deg)
ans <- signif(w / 2 / sin(a * pi / 180), 3)

sc <- num_to_schoice(ans, format = FALSE)
sc$questions <- sprintf("%g N", signif(sc$questions, 3))

# use the same graphics type (pdf, svg, png) as the current xweave() call
typ <- match_exams_device()

## tikz graphic
y_top <- -2 * tan(a * pi / 180)
tikz <- c("\\begin{tikzpicture}",
  "\\draw[thick] (0, 0) -- (6, 0);",
  sprintf("\\draw[thick](1,0) coordinate (A) -- (3, %f) coordinate (B) -- (5, 0) coordinate (C);", y_top),
  sprintf("\\draw[thick] (2, %f) rectangle node[midway, font=\\small]{%d N} (4, %f);", y_top, w, y_top - 1),
  sprintf("\\coordinate (D) at (1, %f); \\coordinate (E) at (5, %f);", y_top, y_top),
  sprintf("\\pic[\"$%d^\\circ$\"scale=0.75, draw, angle eccentricity=2] {angle={A--B--D}};", a),
  sprintf("\\pic[\"$%d^\\circ$\"scale=0.75, draw, angle eccentricity=2] {angle={E--B--C}};", a),
  "\\end{tikzpicture}")
```

Question
========
A sign that weighs $`r w`$ N is supported by two ropes that each makes a $`r a`^\circ$
angle with the horizontal. The sign is not moving. What is the magnitude of the
force exerted by each rope?

\vspace*{1em}

```{r, echo = FALSE, results = "asis"}
include_tikz(tikz, name = "boxes", format = typ, library = c("arrows.meta", "angles", "quotes"))
```

```{r, echo = FALSE, results = "asis"}
answerlist(sc$questions, markup = "markdown")
```


Solution
========
The horizontal components cancel out so the two vertical components must balance
the weight of the sign. (See the example problem on p. 122.)
$$F = \frac{(`r w` N)}{2\sin(`r a`^\circ)} = `r ans` \text{ N}$$


Meta-information
================
exname: Calculate Tension Hanging Sign
extype: schoice
exsolution: `r mchoice2string(sc$solutions)`
exshuffle: 4
