```{r, echo = FALSE, results = "hide"}
f <- sample(10:99, 2) # force (N)
a <- sample (-179:180, 2) # angle (deg)

x <- sum(f * cos(a * pi / 180))
y <- sum(f * sin(a * pi / 180))
ans <- atan2(y, x) * 180 / pi

sc <- num_to_schoice(ans, digits = 1, range = c(-180, 180), format = FALSE)
sc$questions <- sprintf("$%.1f^\\circ$", sc$questions)
```

Question
========
Charlie pulls on a box with $`r fmt(f[1], 1)`$ N of force at $`r a[1]`^\circ$. 
Dan pulls on the the same box with $`r fmt(f[2], 1)`$ N of force at $`r a[2]`^\circ$.
What is the angle of the net force on the box?

```{r, echo = FALSE, results = "asis"}
answerlist(sc$questions, markup = "markdown")
```


Solution
========
The sum of the horizontal components is
$$F_{net, x} = (`r f[1]` N)\cos(`r a[1]`^\circ) + (`r f[2]` N)\cos(`r a[2]`^\circ) = `r x` N$$
The sum of the vertical components is 
$$F_{net, y} = (`r f[1]` N)\sin(`r a[1]`^\circ) + (`r f[2]` N)\sin(`r a[2]`^\circ) = `r y` N$$
The angle of the net force is
$$\theta = \tan^{-1}(`r y` / `r x`)  = `r fmt(ans, 1)`^\circ$$


Meta-information
================
exname: Calculate Net Force Angle
extype: schoice
exsolution: `r mchoice2string(sc$solutions)`
exshuffle: 4
