```{r, echo = FALSE, results = "hide"}
m <- sample(10:99, 2) # masses 1 and 2 (kg)
ans <- 9.8 * abs(m[1] - m[2]) / (m[1] + m[2])

sc <- num_to_schoice(ans, delta = ans/10, format = FALSE)
sc$questions <- sprintf("%g m/s/s", signif(sc$questions, 3))

# use the same graphics type (pdf, svg, png) as the current xweave() call
typ <- match_exams_device()

## tikz graphic
tikz <- c("\\begin{tikzpicture}",
  "\\draw[thick] (0, 0) circle [radius=0.5];",
  "\\draw[thick] (-0.5, 0) -- (-0.5, -1);",
  "\\draw[thick] (0.5, 0) -- (0.5, -2);",
  "\\draw[thick] (-0.9, -1) rectangle node[midway, font=\\small]{$m_1$} (-0.1, -1.5);",
  "\\draw[thick] (0.1, -2) rectangle node[midway, font=\\small]{$m_2$} (0.9, -2.5);",
  "\\end{tikzpicture}")
```

Question
========
Two masses are attached to a lightweight cord that passes over a frictionless 
pulley as shown in the diagram. The values of the masses are $m_1 = `r fmt(m[1], 1)`$ kg 
and $m_2 = `r fmt(m[2], 1)`$ kg. The hanging masses are free to move. 
What is the magnitude of the acceleration of the system?

```{r, echo = FALSE, results = "asis"}
include_tikz(tikz, name = "pulley-system", format = typ)
```

```{r, echo = FALSE, results = "asis"}
answerlist(sc$questions, markup = "markdown")
```


Solution
========
Since the weight of the two masses oppose each other, the net force is the 
difference of the masses times the gravitational field strength. The direction
is of course down toward the heavier side. We can use the absolute value of the
difference to find the magnitude of the acceleration.
$$F_{net} = |m_1 - m_2|g$$

The magnitude of the acceleration is then
$$a = \left| \frac{m_1 - m_2}{m_1 + m_2}\right| g$$
The answer is
$$a = `r signif(ans, 3)` \text{ m/s/s}$$


Meta-information
================
exname: Calculate Pulley System Acceleration
extype: schoice
exsolution: `r mchoice2string(sc$solutions)`
exshuffle: 4
