```{r, echo = FALSE, results = "hide"}
m <- signif(runif(1, 10, 99), 4) # mass (kg)
g <- signif(runif(1, 1, 20), 4) # acceleration of gravity (m/s^2)
w <- signif(m * g, 4) # weight (N)

ans <- signif(w / m, 4) # acceleration of gravity (m/s^2)

sc <- num_to_schoice(ans, delta = 0.01, format = FALSE, digits = 2)
sc$questions <- sprintf("$%g \\mathsf{\\,m/s^2}$", sc$questions)
```

Question
========
You place a `r m`-kg object on a spring scale. If the scale reads `r w` N, what
is the acceleration of gravity at that location? 


```{r, echo = FALSE, results = "asis"}
answerlist(sc$questions, markup = "markdown")
```


Solution
========
The acceleration of gravity ($g$) is related to the mass ($m$) and weight ($W$) 
of objects by the equation $W = mg$. Solving for $g$, we get
$$g = \frac{W}{m} = \frac{`r w` \mathsf{\,N}}{`r m` \mathsf{\,kg}} = `r fmt(ans, 2)` \mathsf{\,m/s^2}$$


Meta-information
================
exname: Calculate g given weight and mass
extype: schoice
exsolution: `r mchoice2string(sc$solutions)`
exshuffle: 4
