```{r, echo = FALSE, results = "hide"}
f <- sample(10:99, 2) # force (N)
a <- sample (-179:180, 2) # angle (deg)

x <- sum(f * cos(a * pi / 180))
y <- sum(f * sin(a * pi / 180))
fnet_ang <- atan2(y, x) * 180 / pi
ans <- ifelse(fnet_ang > 0, fnet_ang - 180, fnet_ang + 180)

sc <- num_to_schoice(ans, digits = 1, range = c(-180, 180), format = FALSE)
sc$questions <- sprintf("$%.1f^\\circ$", sc$questions)
```

Question
========
Two forces act on an object. A $`r fmt(f[1], 1)`$-N force acts at $`r a[1]`^\circ$. A $`r fmt(f[2], 1)`$-N force acts at $`r a[2]`^\circ$.
What is the angle of their equilibrant?

```{r, echo = FALSE, results = "asis"}
answerlist(sc$questions, markup = "markdown")
```


Solution
========
The sum of the horizontal components is
$$F_{net, x} = (`r f[1]` N)\cos(`r a[1]`^\circ) + (`r f[2]` N)\cos(`r a[2]`^\circ) = `r x` N$$
The sum of the vertical components is 
$$F_{net, y} = (`r f[1]` N)\sin(`r a[1]`^\circ) + (`r f[2]` N)\sin(`r a[2]`^\circ) = `r y` N$$
The angle of the net force is
$$\theta_{net} = \tan^{-1}(`r y` / `r x`)  = `r fmt(fnet_ang, 1)`^\circ$$
The direction of the equilibrant is opposite that of the net force so we add or subtract $180^\circ$.
$$\theta_{eq} = `r fmt(fnet_ang + 180, 1)`^\circ$$
Or
$$\theta_{eq} = `r fmt(fnet_ang - 180, 1)`^\circ$$



Meta-information
================
exname: Calculate Equilibrant Angle
extype: schoice
exsolution: `r mchoice2string(sc$solutions)`
exshuffle: 4
