```{r, echo = FALSE, results = "hide"}
m1 <- sample(10:99, 1) # kg
m2 <- m1 * sample(3:12, 1) / 2  # kg
f <- sample(100:999, 1) # N

f2 <- m2 / (m1 + m2) * f # N

sc <- num_to_schoice(f2, delta = f2 / 10, format = FALSE)
sc$questions <- sprintf("%g N", signif(sc$questions, 3))

# use the same graphics type (pdf, svg, png) as the current xweave() call
typ <- match_exams_device()

## tikz graphic
tikz <- c("\\begin{tikzpicture}",
  "\\draw[thick] (0, 0) -- (5, 0);",
  "\\draw[thick] (1, 0) rectangle node[midway, font=\\small]{$m_1$} (2, 1);",
  "\\draw[thick] (2, 0) rectangle node[midway, font=\\small]{$m_2$} (4, 2);",
  sprintf("\\draw[-Stealth, thick] (0, 0.5) -- node[midway, above, font=\\small]{%d N} (1, 0.5);", f),
  "\\end{tikzpicture}")
```

Question
========
Two boxes are in contact with each other on a frictionless table as shown in the diagram. The masses are $m_1 = `r m1`$ kg and $m_2 = `r m2`$ kg. The first box ($m_1$)is pushed with a horizontal force of `r f` N to the right. 
What is the net force on the second box ($m_2$)?

```{r, echo = FALSE, results = "asis"}
include_tikz(tikz, name = "boxes", format = typ, library = c("arrows.meta"))
```

```{r, echo = FALSE, results = "asis"}
answerlist(sc$questions, markup = "markdown")
```


Solution
========
The acceleration of the system of two boxes is
$$a = \frac{\SI{`r f`}{N}}{\SI{`r m1`}{kg} + \SI{`r m2`}{kg}}$$
The net force on $m_2$ is its mass times its acceleration
$$F_{net, 2} = (\SI{`r m2`}{kg}) \left( \frac{\SI{`r f`}{N}}{\SI{`r m1`}{kg} + \SI{`r m2`}{kg}} \right) = \SI{`r signif(f2, 3)`}{N}$$


Meta-information
================
exname: Calculate Net Force on Box 2 Pushing Boxes in Contact
extype: schoice
exsolution: `r mchoice2string(sc$solutions)`
exshuffle: 4
