```{r, echo = FALSE, results = "hide"}
m1 <- sample(10:99, 1) # kg
m2 <- m1 * sample(3:12, 1) / 2 # kg
f <- sample(100:999, 1) # applied force (N)

ans <- m2 / (m1 + m2) * f # N

sc <- num_to_schoice(ans, format = FALSE)
sc$questions <- sprintf("%g N", signif(sc$questions, 3))

# use the same graphics type (pdf, svg, png) as the current xweave() call
typ <- match_exams_device()

## tikz graphic
tikz <- c("\\begin{tikzpicture}",
  "\\draw[thick] (0, 0) -- (8, 0);",
  "\\draw[thick] (5, 0) rectangle node[midway, font=\\small]{$m_1$} (6, 1);",
  "\\draw[thick] (3, 0.5) -- (5, 0.5);",
  "\\draw[thick] (1, 0) rectangle node[midway, font=\\small]{$m_2$} (3, 1);",
  sprintf("\\draw[-Stealth, thick] (6, 0.5) -- node[midway, above, font=\\small]{%d N} (8, 0.5);", f),
  "\\end{tikzpicture}")
```

Question
========
Two boxes connected by a light cord are on a frictionless table as shown in
the diagram. The masses are $m_1 = `r m1` \text{ kg}$ and $m_2 = `r m2` \text{ kg}$.
A `r f`-N force is applied horizontally on the right box. What is the tension in
the cord?

```{r, echo = FALSE, results = "asis"}
include_tikz(tikz, name = "boxes-and-cord", format = typ, library = c("arrows.meta"))
```

```{r, echo = FALSE, results = "asis"}
answerlist(sc$questions, markup = "markdown")
```


Solution
========
The acceleration of the system of two boxes is
$$a = \frac{\SI{`r f`}{N}}{\SI{`r m1`}{kg} + \SI{`r m2`}{kg}}$$
The tension in the cord is the net force on $m_2$ and it is equal to $m_2$ times the acceleration
$$F_{tension} = (\SI{`r m2`}{kg}) \left( \frac{\SI{`r f`}{N}}{\SI{`r m1`}{kg} + \SI{`r m2`}{kg}} \right) = \SI{`r signif(ans, 3)`}{N}$$


Meta-information
================
exname: Calculate Tension in Connected Horizontal Boxes
extype: schoice
exsolution: `r mchoice2string(sc$solutions)`
exshuffle: 4
