```{r, echo = FALSE, results = "hide"}
m <- sample(10:99, 2) # masses 1 and 2 (kg)
ans <- 2 * m[1] * m[2] * 9.8 / (m[1] + m[2])

sc <- num_to_schoice(ans, format = FALSE)
sc$questions <- sprintf("%g N", signif(sc$questions, 3))

# use the same graphics type (pdf, svg, png) as the current xweave() call
typ <- match_exams_device()

## tikz graphic
tikz <- c("\\begin{tikzpicture}",
  "\\draw[thick] (0, 0) circle [radius=0.5];",
  "\\draw[thick] (-0.5, 0) -- (-0.5, -1);",
  "\\draw[thick] (0.5, 0) -- (0.5, -2);",
  "\\draw[thick] (-0.9, -1) rectangle node[midway, font=\\small]{$m_1$} (-0.1, -1.5);",
  "\\draw[thick] (0.1, -2) rectangle node[midway, font=\\small]{$m_2$} (0.9, -2.5);",
  "\\end{tikzpicture}")
```

Question
========
Two masses are attached to a lightweight cord that passes over a frictionless 
pulley as shown in the diagram. The values of the masses are $m_1 = `r fmt(m[1], 1)`$ kg 
and $m_2 = `r fmt(m[2], 1)`$ kg. The hanging masses are free to move. 
What is the tension in the cord?

\vspace*{1em}

```{r, echo = FALSE, results = "asis"}
include_tikz(tikz, name = "pulley-system", format = typ)
```

```{r, echo = FALSE, results = "asis"}
answerlist(sc$questions, markup = "markdown")
```


Solution
========
The acceleration (where $m_1$ moving downward is positive) is
$$a = \left(\frac{m_1 - m_2}{m_1 + m_2}\right) g$$
Newton's Second Law for $m_2$ is $T - m_2 g = m_2 a$. Rearranging for $T$ gives
$$T = m_2 (g + a) = m_2 g \left(1 + \frac{m_1 - m_2}{m_1 + m_2} \right) = \left(\frac{2 m_1 m_2}{m_1 + m_2} \right)g$$
The answer is
$$T = `r signif(ans, 3)` \text{ N}$$


Meta-information
================
exname: Calculate Pulley System Tension
extype: schoice
exsolution: `r mchoice2string(sc$solutions)`
exshuffle: 4
