```{r, echo = FALSE, results = "hide"}
f <- sample(10:99, 2) # force (N)
a <- sample (0:359, 2) # angle (deg)

x <- sum(f * cos(a * pi / 180))
y <- sum(f * sin(a * pi / 180))
ans <- signif(sqrt(x^2 + y^2), 3)

sc <- num_to_schoice(ans, digits = 1, format = FALSE)
sc$questions <- sprintf("%g N", sc$questions)
```

Question
========
Robert pulls on a box with `r fmt(f[1], 1)` N of force at $`r a[1]`^\circ$. 
Steve pulls on the the same box with `r fmt(f[2], 1)` N of force at $`r a[2]`^\circ$.
What is the magnitude of the net force on the box?

```{r, echo = FALSE, results = "asis"}
answerlist(sc$questions, markup = "markdown")
```


Solution
========
The sum of the horizontal components is
$$F_{net, x} = (`r f[1]` N)\cos(`r a[1]`^\circ) + (`r f[2]` N)\cos(`r a[2]`^\circ) = `r x` N$$
The sum of the vertical components is 
$$F_{net, y} = (`r f[1]` N)\sin(`r a[1]`^\circ) + (`r f[2]` N)\sin(`r a[2]`^\circ) = `r y` N$$
The magnitude of the net force is
$$F_{net} = \sqrt{(`r x` N)^2 + (`r y` N)^2} = `r ans` \text{ N}$$


Meta-information
================
exname: Calculate Net Force Magnitude
extype: schoice
exsolution: `r mchoice2string(sc$solutions)`
exshuffle: 4
