```{r, echo = FALSE, results = "hide"}
a <- sample(10:60, 1) # angle of incline (deg)
a_rad <- a * pi / 180
ans <- tan(a_rad)

sc <- num_to_schoice(ans, delta = ans/10, range = c(0, ans*1.5), digits = 3, format = TRUE)
```
Question
========
An box is at rest on an inclined plane. The angle of incline is increased 
slowly. When the angle reaches $`r fmt(a, 1)`^\circ$, the box begins to slide. What is
the coefficient of static friction between the box and the inclined plane?

```{r, echo = FALSE, results = "asis"}
answerlist(sc$questions, markup = "markdown")
```

Solution
========
On an inclined plane, the normal force is equal to the perpendicular component
of the force of gravity:
$$F_N = mg \cos\theta$$
The friction force when the object starts to slide, the maximum static friction
force is reached and it must be equal to the parallel component of the force of gravity:
$$F_f = \mu_s F_N = \mu_s mg \cos \theta = mg \sin \theta$$
Therefore, the coefficient of static friction, $\mu_s$, is:
$$\mu_s = \frac{\sin\theta}{\cos\theta} = \tan \theta = \tan(`r a`^\circ) = `r fmt(ans, 3)`$$


Meta-information
================
exname: Calculate mu Static on Inclined Plane
extype: schoice
exsolution: `r mchoice2string(sc$solutions)`
exshuffle: 4

